\textbf{SYNOPSIS}

### 2017-01-23 second-order-spsa-3.tex
sir corrections + synopsis + abstract

\item $\{\Delta_n^i,\widehat\Delta_n^i, i=1,\ldots,N, n=1,2,\ldots\}$ are i.i.d independent of $\F_n$ and for some $\alpha_0 > 0$ and for all $n,l$ $|\Delta_{nl}|\le \alpha_0$, $\Delta_{nl}$ is symmetrically distributed about 0, $\Delta_{nl}$ are mutually independent across $n$ and $l$ and they satisfy $\E (\Delta_{nl}^{-2})$,$\E (\widehat\Delta_{nl}^{-2}) \le \alpha_0$.

@@

\item For any $\tau >0$ and nonempty $S \subseteq \{1,\ldots,N\}$, there exists a $\rho'(\tau,S)>\tau$ such that 
$$ \limsup_{n\rightarrow \infty} \left| \dfrac{\sum_{i \notin S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}{\sum_{i \in S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}               \right| < 1 \text{ a.s.}$$
for all $|(\theta-\theta^*)_i| < \tau$ when $i \notin S$ and $|(\theta-\theta^*)_i| \ge \rho'(\tau,S)$ when $i\in S$.
\item For some $\alpha_0, \alpha_1, \alpha_2 >0$ and for all $n,l,m$, $\E {\xi_n}^{2} \le \alpha_0$, $\E {\xi_n^{\pm}}^{2} \le \alpha_0$, $\E f(\theta_n)^{2} \le \alpha_1$,  $\E f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)^{2},\E f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)^{2} \le \alpha_1$, 
%$\E \left[ f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)^{2}/ (\Delta_{nl}\widehat\Delta_{nm})^2 \mid \F_n\right]$,
$\E \left[| f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)/ (\Delta_{nl}\widehat\Delta_{nm})|^{2+\alpha_2} \mid \F_n\right]$,
%$\E \left[ f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)^{2}/ (\Delta_{nl}\widehat\Delta_{nm})^2 \mid \F_n\right]$,
$\E \left[ |f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)/ (\Delta_{nl}\widehat\Delta_{nm})|^{2+\alpha_2} \mid \F_n\right]$,
 $\E\left[\left. (\xi_n^+ + \xi_n^- - 2 \xi_n)^2/(\Delta_{nl}\widehat\Delta_{nm})^2 \right| \F_n \right] \le \alpha_1$ 
and $\E \left(\left\| \Upsilon(\overline H_n) \right\|^2 \mid \F_n\right) \le \alpha_1$. 
\item  $\delta_n = \frac{\delta_0}{(n+1)^{\varsigma}}$, where $\delta_0 > 0$ and $0 < \varsigma \le 1/8$.
\end{pvn}
The reader is referred to Section II-B of \cite{prashanth2015rdsa} for a detailed discussion of the above assumptions. We remark here that (A20)-(A27) are identical to those in \cite{prashanth2015rdsa}, while (A28) and (A29) introduce minor additional requirements on $\left\| \Upsilon(\overline H_n) \right\|^2$ and $\delta_n$, respectively and these are inspired from \cite{spall-jacobian}.

@@

We next present a convergence rate result for the special case of a quadratic objective function under the following additional assumptions:
\begin{pvn}
\item  $f$ is quadratic and $\nabla^2 f(x^*) > 0$. 
\item The operator $\Upsilon$ is chosen such that $\E(\parallel \Upsilon(\overline H_n) - \overline H_n\parallel^2) = o(e^{-2wn^{1-r}/(1-r)})$ and \\$\parallel \Upsilon(H) - H \parallel^2 / (1+\parallel H \parallel^2)$ is uniformly bounded.
\end{pvn}
\begin{theorem}(\textbf{2SPSA-3-IH Quadratic case - Convergence rate})
\label{thm:spsaquad-bound}
Assume (A23), (A29), (A30) and (A31) and also that the setting is noise-free. 
Let $b_n = b_0/n^r$, $n=1,2,\ldots,k$, where $1/2 < r < 1$ and $0 < b_0 \leq 1$. For notational simplicity, let $H^*=\nabla^2 f(x^*)$. Letting $\Lambda_k = \overline H_k - H^*$, we have 
\begin{align}
\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}}).
\label{eq:spsaquad-bigo}
\end{align}
\end{theorem}
\begin{proof}
Since the setting is noise-free with a quadratic objective, we can rewrite \eqref{eq:spsahnhat} as follows:
\begin{align}
 \widehat H_n &=    \nabla^2 f(\theta_n) +\Psi_{n}(\nabla^2 f(\theta_n))\nonumber\\
 &=    \nabla^2 f(\theta^*) +\Psi_{n}(\nabla^2 f(\theta^*))\nonumber\\
 &=    H^* +\Psi_{n}(H^* ),\label{eq:spsahnhat-ext}
\end{align}
where $\Psi_n(H)$ is defined in \eqref{eq:psinhatspsa3}.
The proof involves the following steps:
\begin{description}
  \item[Step 1:] Here we prove the MSE convergence of $\overline H_k$, i.e., $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0$ a.s. as $n\rightarrow \infty$.
  \item[Step 2:] We unroll the recursion \eqref{eq:2spsa-3-ih} and then derive a convenient representation for the  $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$.
  \item[Step 3:] We derive the main result in \eqref{eq:spsaquad-bigo} using a proof by contradiction. 
\end{description}
\noindent\textbf{Step 1: MSE convergence of $\overline H_n$} \\
This part in exactly the same manner as part (i) in Theorem 3 of \cite{spall-jacobian}.\\
By rewriting the \eqref{eq:2spsa-3-ih} in the following form
\begin{align}\label{eq:hhatexpanded}
\overline H_{n} &= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - \widehat H_n + \widehat \Psi_n)\nonumber\\
&= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - H^* + \widehat \Psi_n - \Psi_n (H^*)).
\end{align}
The above equation can be thought as a stochastic approximation analogue of \eqref{eq:2spsa-3-ih}. The above stochastic approximation algorithm aimed at finding the roots of the equation $H-H^*=0$. In \eqref{eq:hhatexpanded}, $\E (\widehat \Psi_n - \Psi_n (H^*) | \F_n) = 0 \,\,\ a.s$.  Given a Lyapunov function, one can  the conditions required to show  the mean square convergence of the \eqref{eq:hhatexpanded} from the \cite{nevel1973stochastic}, pp.92-94. It is easy to see that $V(H) = \frac{1}{2} (H-H^*)\tr(H-H^*)$ indeed serves as Lyapunov function. From part (i) in Theorem 3 of \cite{spall-jacobian}, one can check that our algorithm indeed satisfy those conditions,  which in turn implies the $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0 \,\,\,a.s.$ as $n\rightarrow \infty$.

@@

Squaring on both sides and taking expectations, we obtain

@@

The equality above uses the fact that $\E(\Psi_k(\Lambda_{k-1}'))=0$, which get rid of the corresponding cross terms with the first term on RHS of \eqref{lambda-exp}. % %

@@

Where, as in the proof of Theorem 3 of \cite{spall-jacobian}, $\tau(\cdot)$ transforms the $\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')$ in a  fashion and then returns the trace of the resulting $N\times N$ matrix.

@@

\noindent\textbf{Step 3: The big-O result on $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$ convergence} \\
We will use similar argument in part (iii) in Theorem 3 of \cite{spall-jacobian} to show the claim \eqref{eq:spsaquad-bigo}. The idea here is to show that the contradiction exists if RHS of \eqref{eq:spsaquad-bigo} exhibits  any slower rate of decay. Let us assume the following slower rate of decay for the LHS of the \eqref{eq:spsaquad-bigo}.
\begin{align}
\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = d(n) e^{-2b_0n^{1-r} / {1-r}}.
\label{eq:spsaquad-bigocont}
\end{align}
Where $d(n) = o(e^{2b_0n^{1-r} / {1-r}})$. Now we need to show that there is contradiction to show the claim. By using the series of arguments used in part (iii) in Theorem 3 of \cite{spall-jacobian} and applying the condition (A31) we get the following 
\begin{align}
\E (\Lambda_{n}' \otimes \Lambda_{n}') = \E (\Lambda_{n} \otimes \Lambda_{n}) + o(d(n) e^{-2b_0n^{1-r} / {1-r}}).
\label{eq:spsaquad-bigocont2}
\end{align}
Now from the above equation we can write 
\begin{align}
\E (\Lambda_{n-1}' \otimes \Lambda_{n-1}') = O (\text{trace}[\E (\Lambda_{n-1} \tr \Lambda_{n-1})]). 
\label{eq:spsaquad-bigocont3}
\end{align}

Now we can use the this result in RHS of the equation \eqref{eq:thmwts} to show the contradiction. We consider the two cases to show the contradiction. One is where $\frac{d(n)}{n^{2r}} = O(1)$ and another is $lim sup_{n \to \infty} \frac{d(n)}{n^{2r}} = \infty$. We show contradiction for the both cases separately. Let us consider the first case $\frac{d(n)}{n^{2r}} = O(1)$, then
\begin{align}
\text{RHS of \eqref{eq:thmwts}} &= O(1) e^{-2 \Gamma_{1n}} +  O(1) e^{-2 b_0 n^{1-r}/(1-r)} \sum_{i=1}^n \frac{d(i)}{i^{p}} \frac{b_0^2}{i^{2r-p}}\nonumber \\
&= e^{-2b_0n^{1-r} / {1-r}} \left[ O(1) + O(1) \sum_{i =1}^n \frac{1}{i^{2r-p}}\right].
\label{eq:spsaquad-bigocont4}
\end{align}
where there exist  $0 < p \le 2r$, $0 < \epsilon < 2r -1$ such that $\frac{d(n)}{i^{p}} = O(1)$ and $lim sup_{n \to \infty} \frac{d(n)}{n^{p-\epsilon}} = \infty$. In \eqref{eq:spsaquad-bigocont4}, the first equality uses \eqref{eq:spsaquad-bigocont} and \eqref{eq:spsaquad-bigocont3}.

Now there exists a subsequence $\{i_1,\ldots,i_n\}$ such that $ \frac{d(i_n)}{i_n^{p-\epsilon}} = \infty$ as $n \to \infty$. Now LHS of \eqref{eq:thmwts} satisfies $LHS(i_n) \ge C i_n^{p-\epsilon} e^{-2b_0 i_n^{1-r} / {1-r}}$ for some $C > 0$. Now we have $\frac{LHS(i_n)}{RHS(i_n)} \to 0$ because  $0 < \epsilon < 2r -1$. It is contradiction since $LHS(n) = RHS(n)$ for all $n$.

Now consider the second case where $lim sup_{n \to \infty} \frac{d(n)}{n^{2r}} = \infty$. There exists a subsequence $\{i_1,\ldots,i_n\}$ such that $ \frac{d(i_n)}{i_n^{2r}} \ge \frac{d(i)}{i^{2r}}$ as $i \le i_n$. Then for some $C >0$ the RHS of \eqref{eq:thmwts} satisfies the following 
\begin{align}
\text{RHS}(i_n)\,\,\,  \text{of}  \,\,\,\eqref{eq:thmwts} &= O(1) e^{-2 \Gamma_{1i_n}} +  O(1) e^{-2 b_0 i_n^{1-r}/(1-r)} \left[\sum_{i=1}^{i_n} e^{2 b_0 i^{1-r}/(1-r)} \frac{b_0^2}{i^{2r}} \E (\Lambda_{n} \otimes \Lambda_{n}) \right]\nonumber \\
&\le C e^{-2b_0n^{1-r} / {1-r}} \left[ 1 + O(1) \sum_{i =1}^{i_n} \frac{d(i)}{i^{2r}}\right]\nonumber \\
&\le C e^{-2b_0n^{1-r} / {1-r}} \left[ 1 + \frac{d(i_n)}{{i_n}^{2r}}\right].
\label{eq:spsaquad-bigocont5}
\end{align}
Where $\text{RHS}(i_n)$ denotes, RHS after the algorithm is iterated for $i_n$ times. From the equation \eqref{eq:spsaquad-bigocont}, the  LHS of \eqref{eq:thmwts} after $i_n$ iterations is $d(i_n) e^{-2b_0 i_n^{1-r} / {1-r}}$. By substituting \eqref{eq:spsaquad-bigocont} and \eqref{eq:spsaquad-bigocont5}, in $\frac{RHS(i_n)}{LHS(i_n)}$ then $\frac{RHS(i_n)}{LHS(i_n)} \to 0$ as $n \to \infty$. It is contradiction since $LHS(n) = RHS(n)$ for all $n$. Hence the claim $\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}})$ follows.
\end{proof}

>>>>

\item $\{\Delta_n^i,\widehat\Delta_n^i, i=1,\ldots,N, n=1,2,\ldots\}$ are i.i.d independent of $\F_n$ and for some $\alpha_3 > 0$ and for all $n,l$ $|\Delta_{nl}|\le \alpha_3$, $\Delta_{nl}$ is symmetrically distributed about 0, $\Delta_{nl}$ are mutually independent across $n$ and $l$ and they satisfy $\E (\Delta_{nl}^{-2})$, $\E (\widehat\Delta_{nl}^{-2}) \le \alpha_3$.

@@

\item For any $\tau >0$ and nonempty $S \subseteq \{1,\ldots,N\}$, there exists a $\rho'(\tau,S)>\tau$ such that 
$$ \limsup_{n\rightarrow \infty} \left| \dfrac{\sum_{i \notin S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}{\sum_{i \in S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}               \right| < 1 \text{ a.s.}$$
for all $|(\theta-\theta^*)_i| < \tau$ when $i \notin S$ and $|(\theta-\theta^*)_i| \ge \rho'(\tau,S)$ when $i\in S$.
\item For some $\alpha_7, \alpha_8, \alpha_9 >0$ and for all $n,l,m$, $\E {\xi_n}^{2} \le \alpha_7$, $\E {\xi_n^{\pm}}^{2} \le \alpha_7$, $\E f(\theta_n)^{2} \le \alpha_8$,  $\E f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)^{2},\E f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)^{2} \le \alpha_8$, 
%$\E \left[ f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)^{2}/ (\Delta_{nl}\widehat\Delta_{nm})^2 \mid \F_n\right]$,
$\E \left[| f(\theta_n + \delta_n \Delta_n + \delta_n \widehat \Delta_n)/ (\Delta_{nl}\widehat\Delta_{nm})|^{2+\alpha_9} \mid \F_n\right]$,
%$\E \left[ f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)^{2}/ (\Delta_{nl}\widehat\Delta_{nm})^2 \mid \F_n\right]$,
$\E \left[ |f(\theta_n - \delta_n \Delta_n - \delta_n \widehat \Delta_n)/ (\Delta_{nl}\widehat\Delta_{nm})|^{2+\alpha_9} \mid \F_n\right]$,
 $\E\left[\left. (\xi_n^+ + \xi_n^- - 2 \xi_n)^2/(\Delta_{nl}\widehat\Delta_{nm})^2 \right| \F_n \right] \le \alpha_8$ 
and $\E \left(\left\| \Upsilon(\overline H_n) \right\|^2 \mid \F_n\right) \le \alpha_8$. 
\item  $\delta_n = \frac{\delta_0}{(n+1)^{\varsigma}}$, where $\delta_0 > 0$ and $0 < \varsigma \le 1/8$.
\end{pvn}
The reader is referred to Section II-B of \cite{prashanth2015rdsa} for a detailed discussion of the above assumptions. We remark here that (A20)-(A27) are identical to those in \cite{prashanth2015rdsa}, while (A28) and (A29) introduce minor additional requirements on $\left\| \Upsilon(\overline H_n) \right\|^2$ and $\delta_n$, respectively and these are inspired from \cite{spall-jacobian}.

@@

We next present a convergence rate result for the special case of a quadratic objective function under the following additional assumptions:
\begin{pvn}
\item  $f$ is quadratic and $\nabla^2 f(\theta^*) > 0$. 
\item The operator $\Upsilon$ is chosen such that $\E(\parallel \Upsilon(\overline H_n) - \overline H_n\parallel^2) = o(e^{-2wn^{1-r}/(1-r)})$ and \\$\parallel \Upsilon(H) - H \parallel^2 / (1+\parallel H \parallel^2)$ is uniformly bounded.
\end{pvn}
\begin{theorem}(\textbf{2SPSA-3-IH Quadratic case - Convergence rate})
\label{thm:spsaquad-bound}
Assume (A23), (A29), (A30) and (A31) and also that the setting is noise-free. 
Let $b_n = b_0/n^r$, $n=1,2,\ldots,k$, where $1/2 < r < 1$ and $0 < b_0 \leq 1$. For notational simplicity, let $H^*=\nabla^2 f(\theta^*)$. Letting $\Lambda_k = \overline H_k - H^*$, we have 
\begin{align}
\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}}).
\label{eq:spsaquad-bigo}
\end{align}
\end{theorem}
\begin{proof}
Since the setting is noise-free with a quadratic objective, we can rewrite \eqref{eq:spsahnhat} as follows:
\begin{align}
 \widehat H_n &=    \nabla^2 f(\theta_n) +\Psi_{n}(\nabla^2 f(\theta_n))\nonumber\\
 &=    \nabla^2 f(\theta^*) +\Psi_{n}(\nabla^2 f(\theta^*))\nonumber\\
 &=    H^* +\Psi_{n}(H^* ),\label{eq:spsahnhat-ext}
\end{align}
where $\Psi_n(H)$ is defined in \eqref{eq:psinhatspsa3}.
The proof involves the following steps:
\begin{description}
  \item[Step 1:] Here we prove the MSE convergence of $\overline H_k$, i.e., $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0$ a.s. as $n\rightarrow \infty$.
  \item[Step 2:] We unroll the recursion \eqref{eq:2spsa-3-ih} and then derive a convenient representation for the  $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$.
  \item[Step 3:] We derive the main result in \eqref{eq:spsaquad-bigo} using a proof by contradiction. 
\end{description}
\noindent\textbf{Step 1: MSE convergence of $\overline H_n$} \\
This part of the proof follows along similar lines as  part (i) in Theorem 3 of \cite{spall-jacobian}.\\
By rewriting the \eqref{eq:2spsa-3-ih} in the following form
\begin{align}\label{eq:hhatexpanded}
\overline H_{n} &= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - \widehat H_n + \widehat \Psi_n)\nonumber\\
&= \overline H_{n-1} - b_{n} ( \overline H_{n-1} - H^* + \widehat \Psi_n - \Psi_n (H^*)).
\end{align}
The above equation can be thought as a stochastic approximation analogue of \eqref{eq:2spsa-3-ih}. The above stochastic approximation algorithm is aimed at finding the roots of the equation $H-H^*=0$. In \eqref{eq:hhatexpanded}, $\E (\widehat \Psi_n - \Psi_n (H^*) | \F_n) = 0 \,\,\ a.s$.  Given a Lyapunov function, one can  get the conditions required to show  the mean square convergence of the \eqref{eq:hhatexpanded} from \cite{nevel1973stochastic}, pp.92-94. It is easy to see that $V(H) = \frac{1}{2} (H-H^*)\tr(H-H^*)$ indeed serves as Lyapunov function. From part (i) in Theorem 3 of \cite{spall-jacobian}, one can check that our algorithm indeed satisfies those conditions,  which in turn implies that $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0 \,\,\,a.s.$ as $n\rightarrow \infty$.

@@

It follows from \eqref{lambda-exp} that 

@@

The equality above uses the fact that $\E(\Psi_k(\Lambda_{k-1}'))=0$, which gets rid of the corresponding cross terms with the first term on RHS of \eqref{lambda-exp}. % %

@@

whereas in the proof of Theorem 3 of \cite{spall-jacobian}, $\tau(\cdot)$ transforms the $\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')$ in a  fashion and then returns the trace of the resulting $N\times N$ matrix.

@@

\noindent\textbf{Step 3: The big-O result on $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$ convergence} \\
We will use similar argument in part (iii) in Theorem 3 of \cite{spall-jacobian} to show the claim \eqref{eq:spsaquad-bigo}. The idea here is to show that the contradiction exists if RHS of \eqref{eq:spsaquad-bigo} exhibits  any slower rate of decay. Let us assume the following slower rate of decay for the LHS of \eqref{eq:spsaquad-bigo}.
\begin{align}
\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = d(n) e^{-2b_0n^{1-r} / {1-r}},
\label{eq:spsaquad-bigocont}
\end{align}
where $d(n) = o(e^{2b_0n^{1-r} / {1-r}})$. Now we will to show that there is a contradiction. By using the series of arguments used in part (iii) in Theorem 3 of \cite{spall-jacobian} and applying the condition (A31) we get the following: 
\begin{align}
\E (\Lambda_{n}' \otimes \Lambda_{n}') = \E (\Lambda_{n} \otimes \Lambda_{n}) + o(d(n) e^{-2b_0n^{1-r} / {1-r}}).
\label{eq:spsaquad-bigocont2}
\end{align}
Now from the above equation we can write 
\begin{align}
\E (\Lambda_{n-1}' \otimes \Lambda_{n-1}') = O (\text{trace}[\E (\Lambda_{n-1} \tr \Lambda_{n-1})]). 
\label{eq:spsaquad-bigocont3}
\end{align}

Now we can use the result in the RHS of equation \eqref{eq:thmwts} to show the contradiction. We consider two cases to show the contradiction. The first is where $\frac{d(n)}{n^{2r}} = O(1)$ and the other is $lim sup_{n \to \infty} \frac{d(n)}{n^{2r}} = \infty$. We show contradiction for the both cases separately. Let us consider the first case, i.e., $\frac{d(n)}{n^{2r}} = O(1)$, Then
\begin{align}
\text{RHS of \eqref{eq:thmwts}} &= O(1) e^{-2 \Gamma_{1n}} +  O(1) e^{-2 b_0 n^{1-r}/(1-r)} \sum_{i=1}^n \frac{d(i)}{i^{p}} \frac{b_0^2}{i^{2r-p}}\nonumber \\
&= e^{-2b_0n^{1-r} / {1-r}} \left[ O(1) + O(1) \sum_{i =1}^n \frac{1}{i^{2r-p}}\right],
\label{eq:spsaquad-bigocont4}
\end{align}
where there exist  $0 < p \le 2r$, $0 < \epsilon < 2r -1$ such that $\frac{d(n)}{i^{p}} = O(1)$ and $lim sup_{n \to \infty} \frac{d(n)}{n^{p-\epsilon}} = \infty$. In \eqref{eq:spsaquad-bigocont4}, the first equality uses \eqref{eq:spsaquad-bigocont} and \eqref{eq:spsaquad-bigocont3}.

Now there exists a subsequence $\{i_1,\ldots,i_n\}$ such that $ \frac{d(i_n)}{i_n^{p-\epsilon}} = \infty$ as $n \to \infty$. Now LHS of \eqref{eq:thmwts} satisfies $LHS(i_n) \ge C i_n^{p-\epsilon} e^{-2b_0 i_n^{1-r} / {1-r}}$ for some $C > 0$. Now we have $\frac{LHS(i_n)}{RHS(i_n)} \to 0$ because  $0 < \epsilon < 2r -1$. This leads to a contradiction since $LHS(n) = RHS(n)$ for all $n$.

Now consider the second case where $lim sup_{n \to \infty} \frac{d(n)}{n^{2r}} = \infty$. There exists a subsequence $\{i_1,\ldots,i_n\}$ such that $ \frac{d(i_n)}{i_n^{2r}} \ge \frac{d(i)}{i^{2r}}$ as $i \le i_n$. Then for some $C >0$ the RHS of \eqref{eq:thmwts} satisfies the following:
\begin{align}
\text{RHS}(i_n)\,\,\,  \text{of}  \,\,\,\eqref{eq:thmwts} &= O(1) e^{-2 \Gamma_{1i_n}} +  O(1) e^{-2 b_0 i_n^{1-r}/(1-r)} \left[\sum_{i=1}^{i_n} e^{2 b_0 i^{1-r}/(1-r)} \frac{b_0^2}{i^{2r}} \E (\Lambda_{n} \otimes \Lambda_{n}) \right]\nonumber \\
&\le C e^{-2b_0n^{1-r} / {1-r}} \left[ 1 + O(1) \sum_{i =1}^{i_n} \frac{d(i)}{i^{2r}}\right]\nonumber \\
&\le C e^{-2b_0n^{1-r} / {1-r}} \left[ 1 + \frac{d(i_n)}{{i_n}^{2r}}\right],
\label{eq:spsaquad-bigocont5}
\end{align}
where $\text{RHS}(i_n)$ denotes, RHS after the algorithm is iterated for $i_n$ times. From the equation \eqref{eq:spsaquad-bigocont}, the  LHS of \eqref{eq:thmwts} after $i_n$ iterations is $d(i_n) e^{-2b_0 i_n^{1-r} / {1-r}}$. By substituting \eqref{eq:spsaquad-bigocont} and \eqref{eq:spsaquad-bigocont5}, in $\frac{RHS(i_n)}{LHS(i_n)}$, it turns out that $\frac{RHS(i_n)}{LHS(i_n)} \to 0$ as $n \to \infty$. This results in a contradiction since $LHS(n) = RHS(n)$ for all $n$. Hence the claim $\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}})$ follows.
\end{proof}

### 2017-01-23 secorder-rdsa-ih.tex
sir corrections + synopsis + abstract

\item For any $\tau >0$ and nonempty $S \subseteq \{1,\ldots,N\}$, there exists a $\rho'(\tau,S)>\tau$ such that 
$$ \limsup_{n\rightarrow \infty} \left| \dfrac{\sum_{i \notin S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}{\sum_{i \in S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}               \right| < 1 \text{ a.s.}$$
for all $|(\theta-\theta^*)_i| < \tau$ when $i \notin S$ and $|(\theta-\theta^*)_i| \ge \rho'(\tau,S)$ when $i\in S$.
\item For some $\alpha_0, \alpha_1>0$ and for all $n$, $\E {\xi_n}^{2} \le \alpha_0$, $\E {\xi_n^{\pm}}^{2} \le \alpha_0$, $\E f(\theta_n)^{2} \le \alpha_1$,  $\E f(\theta_n\pm \delta_n d_n)^{2} \le \alpha_1$ and $\E \left(\left\| \Upsilon(\overline H_n) \right\|^2 \mid \F_n\right) \le \alpha_1$. 
\item  $\delta_n = \frac{\delta_0}{(n+1)^{\varsigma}}$, where $\delta_0 > 0$ and $0 < \varsigma \le 1/8$.
\end{pvn}
The reader is referred to Section II-B of \cite{prashanth2015rdsa} for a detailed discussion of the above assumptions. We remark here that (A8)-(A15) are identical to assumptions in \cite{prashanth2015rdsa}, while (A16) and (A17) introduce minor additional requirements on $\left\| \Upsilon(\overline H_n )\right\|^2$ and $\delta_n$, respectively and these are inspired from \cite{spall-jacobian}.

>>>>

\item For any $\tau >0$ and nonempty $S \subseteq \{1,\ldots,N\}$, there exists a $\rho'(\tau,S)>\tau$ such that 
$$ \limsup_{n\rightarrow \infty} \left| \dfrac{\sum_{i \notin S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}{\sum_{i \in S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}               \right| < 1 \text{ a.s.}$$
for all $|(\theta-\theta^*)_i| < \tau$ when $i \notin S$ and $|(\theta-\theta^*)_i| \ge \rho'(\tau,S)$ when $i\in S$.
\item For some $\alpha_5, \alpha_6>0$ and for all $n$, $\E {\xi_n}^{2} \le \alpha_5$, $\E {\xi_n^{\pm}}^{2} \le \alpha_5$, $\E f(\theta_n)^{2} \le \alpha_6$,  $\E f(\theta_n\pm \delta_n d_n)^{2} \le \alpha_6$ and $\E \left(\left\| \Upsilon(\overline H_n) \right\|^2 \mid \F_n\right) \le \alpha_6$. 
\item  $\delta_n = \frac{\delta_0}{(n+1)^{\varsigma}}$, where $\delta_0 > 0$ and $0 < \varsigma \le 1/8$.
\end{pvn}
The reader is referred to Section II-B of \cite{prashanth2015rdsa} for a detailed discussion of the above assumptions. We remark here that (A8)-(A15) are identical to assumptions in \cite{prashanth2015rdsa}, while (A16) and (A17) introduce minor additional requirements on $\left\| \Upsilon(\overline H_n )\right\|^2$ and $\delta_n$, respectively and these are inspired from \cite{spall-jacobian}.
